\begin{abstract}

信息抽取表示自动的从文本中抽取出结构化的信息，比如实体，实体间的关系或者包含在有噪音的非结构化文本中的属性描述性实体，将非结构化文本抽取出有用的信息存储在结构化形式中，比如表格，XML，图谱，有着非常重要的价值，信息抽取是构建知识图谱的基础理论和实践支撑。信息抽取又包含了若干个子问题，比如，命名体识别，开放域信息抽取，关系抽取以及文本分割。分割式信息抽取是一个特殊的信息抽取问题，它是通过分割半结构化文本信息来抽取出隐含其中的属性值。

目前主流的解决方案是采用机器学习的方法，包括使用人工标注的训练集使用监督式机器学习方案，或者利用事先存在的知识库来辅助实施非监督式式的机器学习方案，在非监督式方法中，一个杰出的解决方案是借助于知识库，讲整个信息抽取流程分为分割，匹配，调整等若干个模块，取得了目前为止最好的表现。但是，当采用监督式方案是，获取标注好的训练集要花费非常昂贵的代价，并且往往只限制在某个领域内。而通过知识库辅助的方案，则会出现两个主要问题，1. 固定领域文本的属性顺序限制在固定的顺序上，2.匹配准确率底下。

为了解决上述方案的问题，本文提出了结合深度学习和概率模型的方案，充分利用深度学习强大的特征抽取和组合能力，并结合概率模型的适用性和可解释性。构建了完整的高效的解决方案。本文提出的方法同样借助知识库来克服人工标注的问题，并且有效克服了匹配率底下以及限定属性顺序的问题。具体研究内容如下：

(1)如何选择深度学习模型，如何将深度学习模型与概率模型完美的结合起来，并探索深度学习模型构建和优化的策略，包括构建有效的丰富的特征。

(2)提出了基于卷积神经网络的贪婪式概率匹配算法。本算法采用深度卷积神经网络模型，提出了一种贪婪式的概率匹配算法，并在抽取过程中学习出一个双向的序列与位置模型来完成抽取任务，采用了步步提升的设计方案，有效的解决了上述的问题，经过比较F1值取得了非常明显的提升，并在抽取效率上也有非常好的表现。

(3)提出 CNN+LSTM+attention model+CRF的解决方案

\keywords{深度学习, 信息抽取, 文本分割}

\end{abstract}

\vspace{-6.4pt}
\soochowauthor{胡猛\quad}

\soochowtutor{李直旭\quad}

\begin{englishabstract}

With the rapid development of information technology, the data from different field explosively grow, which makes data quality problems increasingly highlight, such as data distortion, data staleness, data missing, inconsistent data expression and so on. This paper mainly do research on one of the important data quality subjects, so-called Entity Matching (EM for short). EM aims at identifying records referring to the same entity within or across databases.

So far, most existing EM algorithms depend on string similarity metrics to measure the similarity between key attribute values of entities and then make decisions according to a predefined similarity threshold. But an arbitrary threshold is bad for either the matching precision or the recall.

So as to solve the problems of the existing methods, we propose entity matching algorithms based on polymorphic non-key attributes by analysing textual data and computing similarity do EM. Our methods are orthodox to the existing EM methods based on key attributes. We mainly pay attention on how to use non-key attributes smartly to improve the precision and recall of EM based on key attribute only. More details are shown as follows:
%
\begin{enumerate}[(1)]
\item We focus on the problem of EM in the paper. Some existing EM methods are introduced here and the advantages and disadvantages of them are also analysed.

\item We propose non-key attributes based EM algorithms which select non-key attributes according to their identification ability to do EM. With the proposed methods, we can not only solve the problem of different expression but also overcome the problem of missing values.

\item We propose textual data based EM algorithms which mine the key information from textual data. The precision and recall of EM using the proposed methods are greatly improved .
\end{enumerate}

We demonstrate the effectiveness and availability of the proposed methods on on real-world datasets.
Our empirical study shows that our proposed EM methods outperform the state-of-the-art EM methods by reaching a higher EM precision and recall. And the efficiency of EM is also improved greatly by employing the proposed data block algorithm to reduce the times of comparison.

\englishkeywords{Data Quality, Entity Matching, Polymorphic Non-key Attributes Data, Accuracy, Efficiency}

\end{englishabstract}

\ensoochowauthor{Qiang Yang\quad }

\ensoochowtutor{~~Zhixu Li~~\quad}
